Learning complex models with invertible neural networks: a likelihood-free Bayesian approach

### 2019-07-15 latex/paper_main.tex
Splatter done

In what follows, we apply the method to a toy Bayesian regression example with conjugate priors, and then use it to estimate the parameters of challenging models from population dynamics, cognitive science, epidemiology, and genetics. Code for reproducing the results on all following examples is freely available at: \href{https://github.com/stefanradev93/cINN}{https://github.com/stefanradev93/cINN}.

@@

To assess the performance of our method on the following application examples, we consider a number of different metrics. To assess the precision of point estimates (posterior means), we compute the normalized root mean squared error (NRMSE) and the coefficient of determination ($R^{2}$) between estimated and true parameter values. To assess the recovery of the full posterior, we compute the Kullback-Leibler (KL) divergence \cite{hershey2007approximating} between the true and the approximate distributions for the toy example, and use simulation-based calibration (SBC, \cite{talts2018validating}) for the other examples where the analytic posterior is not available in closed-form. Details for computing the NRMSE, $R^2$, and SCB can be found in the \textbf{SI}.

@@

As a proof-of-concept, we demonstrate the utility of our method in recovering the true analytic posteriors of the regression coefficients of a conjugate Bayesian regression model. To set the stage, assume we have observed a dataset $\boldsymbol{D} = \{(\boldsymbol{x}^{(i)},y^{(i)})\}_{i=1}^{n}$ with $\boldsymbol{x} \in \mathbb{R}^{d}$ and $y \in \mathbb{R}$. We stack all $\boldsymbol{x}^{(i)}$ row-wise in a design matrix $\boldsymbol{X}$ and model the vector of outcomes $\boldsymbol{y}$ as being conditionally Gaussian given $\boldsymbol{X}$, that is, $\boldsymbol{y} \sim \mathcal{N}_{n}(\boldsymbol{X}\boldsymbol{\theta},a^{-1}\boldsymbol{I})$ where $\boldsymbol{\theta} \in \mathbb{R}^{d}$ and $a$ is the precision (inverse noise variance, $a \equiv 1/\sigma_{y}^{2}$). We place a $d$-dimensional diagonal Gaussian prior on the regression coefficients centered at $0$: $\boldsymbol{\theta} \sim \mathcal{N}_{d}(\boldsymbol{0},b^{-1}\boldsymbol{I})$ where $b$ is the precision of the prior ($b \equiv 1/\sigma_{\boldsymbol{\theta}}^{2}$). Thus, the likelihood $p(\boldsymbol{D}|\boldsymbol{\theta})$ admits the following proportionality:
\begin{align*}
p(\boldsymbol{D}|\boldsymbol{\theta}) \propto \exp\left(-\frac{a}{2}\left(\boldsymbol{y}-\boldsymbol{X}\boldsymbol{\theta}\right)^{T}\left(\boldsymbol{y} - \boldsymbol{X}\boldsymbol{\theta}\right)\right) \numberthis 
\end{align*}
Since the prior of $\boldsymbol{\theta}$ is conjugate to the likelihood (both are Gaussian distributions), the posterior of $\boldsymbol{\theta}$ is also Gaussian, given by:
\begin{align*}
p(\boldsymbol{\theta}|\boldsymbol{D}) \propto \exp\left(-\frac{a}{2}\left(\boldsymbol{y}-\boldsymbol{X}\boldsymbol{\theta}\right)^{T}\left(\boldsymbol{y} - \boldsymbol{X}\boldsymbol{\theta}\right)-\frac{b}{2}\boldsymbol{\theta}^{T}\boldsymbol{\theta}\right) \numberthis 
\end{align*}
Therefore, the posterior has the form $p(\boldsymbol{\theta}|\boldsymbol{D}) = \mathcal{N}_{d}(\boldsymbol{\theta}|\boldsymbol{\mu},\boldsymbol{\Lambda}^{-1})$ where $\boldsymbol{\Lambda}$ denotes the posterior precision matrix (inverse covariance matrix), $\boldsymbol{\mu}$ the posterior mean vector, which are computed as follows:
\begin{align*}
\boldsymbol{\Lambda} &= a\boldsymbol{X}^{T}\boldsymbol{X} + b\boldsymbol{I} \numberthis \\
\boldsymbol{\mu} &= a\boldsymbol{\Lambda}^{-1}\boldsymbol{X}^{T}\boldsymbol{y} \numberthis
\end{align*} 
Thus, for known $a$ and $b$, the posterior can be easily computed. Even though in real-world applications $a$ is usually not known and a hierarchical model is used instead, the current example is good for testing the utility of our method.

@@

What if the data does not contain information about a particular parameter? In this case, any good estimation method should detect this, and return the prior of the particular parameter. To test this, we append a random uniform variable $u \sim \mathcal{U}(0, 1)$ to the parameter vector $\boldsymbol{\theta}$ and train the model with this additional dummy parameter. We expect that the networks learn to ignore this dummy parameter, that is, the estimated posterior of $u$ is (approximately) equal to the uniform prior.

@@

During training of the networks, we simulate time-series from the stochastic SIR model with varying lengths. The number of time points $T$ is drawn from a uniform distribution $T \sim \mathcal{U}(200, 500)$ at each training iteration (see the \textbf{SI} for more details about the simulation). Usually, at lower $T$s, the system has not converged to an equilibrium (i.e., not all individuals have transitioned from being $I$ to $R$). Thus, it is especially interesting to see if our method can recover the parameters, even if the process dynamics are still unfolding over time. Training the networks took approx. half a day with the active learning approach. Inference on $1000$ datasets with $2000$ posterior samples per parameter took approx. $1.1$ seconds.

@@

\subsection*{Example 4 - Single-Cell RNA Sequencing}
Single-cell RNA sequencing (scRNA-seq) is a method to uncover the dynamics of gene expression within single cells \cite{zappia2017splatter, ozsolak2011rna}. Simulation models for scRNA-seq attempt to mimic the process of sequencing real data samples by combining statistical and algorithmic procedures. The recently developed \textit{Splat} simulation model \cite{zappia2017splatter} implements a hierarchical model where the mean expression levels for multiple genes are samples from a Gamma distribution, and the number of times a gene has been sequenced in a cell is then sampled from a Poisson distribution. The output of the \textit{Splat} simulation is thus a matrix $\boldsymbol{X}$ of \textit{Gene x Cell} counts. \autoref{fig:Fig.7a} depicts the \textit{Splat} algorithm for simulating scRNA-seq data \cite{zappia2017splatter}.
\begin{table} 
\centering
\caption{Splat target parameters estimated by our method}
\begin{tabular}{lll}
Parameter & Name & Description\\
\midrule
$\alpha$ & Mean shape & Shape of the mean gene expression gamma distribution \\
$\beta$ & Mean rate & Rate of the mean gene expression gamma distribution \\
$\mu^{L}$ & Library size location & Location of the library size log-normal distribution \\
$\sigma^{L}$ & Library size scale & Scale of the library size log-normal distribution \\
$\pi^{O}$ & Outlier probability & Probability that a gene is an expression outlier \\
$\mu^{O}$ & Outlier location & Location of the expression outlier factor log-normal distribution \\
$\sigma^{O}$ & Outlier scale & Scale of the expression outlier factor log-normal distribution \\
$\phi$ & Common BCV & Common BCV dispersion across all genes \\
\bottomrule
\end{tabular}
\label{table:Table 1}
\end{table}
As a last example for our method, we use simulations from the \textit{Splat} model and attempt to recover the data-generating parameters. We simulate $500\ 000$  \textit{Gene x Cell} count matrices with different parameter settings (see \textbf{SI} for details of the simulation) and discard implausible simulations (e.g., matrices where more than $90\%$ of the counts are $0$). Each count matrix contains the information about $20$ genes sequenced in $20$ different cells, that is, each $\boldsymbol{X} \in \mathbb{R}^{20\times20}$. The parameters considered for estimation, along with a short description, are listed in \autoref{table:Table 1}. The parameter estimation task is thus to recover $\boldsymbol{\theta} = (\alpha,\beta,\mu^{L},\sigma^{L},\pi^{O},\mu^{O},\sigma^{O},\phi)$ from an observed count matrix $\boldsymbol{X}$. We train the networks for 50 epochs through the entire dataset and evaluate the performance on a separate validation set of $500$ count matrices.
\begin{figure}[H]
\centering
\begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Splatter_plot.png}
    \caption{The \textit{Splat} simulation diagram. Adapted after \cite{zappia2017splatter}.}
    \label{fig:Fig.7a}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Splatter_scatter.png}
    \caption{Parameter recovery }
    \label{fig:Fig.7b}
\end{subfigure}
\caption[short]{Results on the \textit{Splat} scRNA simulation model. \textbf{(a)} The \textit{Splat} simulation diagram; \textbf{(b)} Parameter recovery.} \label{fig:Fig.7}
\end{figure}
The results on the scRNA example are depicted in \autoref{fig:Fig.7}. We observe excellent parameter recovery on the validation set. \textbf{TODO: Train the full method. These results are preliminary}.

>>>>

In what follows, we apply the method to a toy Bayesian regression example with conjugate priors, and then use it to estimate the parameters of challenging models from population dynamics, cognitive science, epidemiology, and genetics.

@@

To assess the performance of our method on the following application examples, we consider a number of different metrics. To assess the precision of point estimates (posterior means), we compute the normalized root mean squared error (NRMSE) and the coefficient of determination ($R^{2}$) between estimated and true parameter values. To assess the recovery of the full posterior, we compute the Kullback-Leibler (KL) divergence \cite{hershey2007approximating} between the true and the approximate distributions for the toy example, and use simulation-based calibration (SBC, \cite{talts2018validating}) for the other examples where the analytic posterior is not available in closed-form. Details for computing the NRMSE, $R^2$, and SCB can be found in the \textbf{SI}. Code for reproducing the results on all following examples, as well as all network implementations, is freely available at: \href{https://github.com/stefanradev93/cINN}{https://github.com/stefanradev93/cINN}.

@@

As a proof-of-concept, we demonstrate the utility of our method in recovering the true analytic posteriors of the regression coefficients of a conjugate Bayesian regression model. To set the stage, assume we have observed a dataset $\boldsymbol{D} = \{(\boldsymbol{x}^{(i)},y^{(i)})\}_{i=1}^{n}$ with $\boldsymbol{x} \in \mathbb{R}^{d}$ and $y \in \mathbb{R}$. We stack all $\boldsymbol{x}^{(i)}$ row-wise in a design matrix $\boldsymbol{X}$ and model the vector of outcomes $\boldsymbol{y}$ as being conditionally Gaussian given $\boldsymbol{X}$, that is, $\boldsymbol{y} \sim \mathcal{N}_{n}(\boldsymbol{X}\boldsymbol{\theta},a^{-1}\boldsymbol{I})$ where $\boldsymbol{\theta} \in \mathbb{R}^{d}$ and $a$ is the precision (inverse noise variance, $a \equiv 1/\sigma_{y}^{2}$). We place a $d$-dimensional diagonal Gaussian prior on the regression coefficients centered at $0$: $\boldsymbol{\theta} \sim \mathcal{N}_{d}(\boldsymbol{0},b^{-1}\boldsymbol{I})$ where $b$ is the precision of the prior ($b \equiv 1/\sigma_{\boldsymbol{\theta}}^{2}$). Thus, the likelihood $p(\boldsymbol{D}|\boldsymbol{\theta})$ admits the following proportionality:
\begin{align*}
p(\boldsymbol{D}|\boldsymbol{\theta}) \propto \exp\left(-\frac{a}{2}\left(\boldsymbol{y}-\boldsymbol{X}\boldsymbol{\theta}\right)^{T}\left(\boldsymbol{y} - \boldsymbol{X}\boldsymbol{\theta}\right)\right) \numberthis 
\end{align*}
Since the prior of $\boldsymbol{\theta}$ is conjugate to the likelihood (both are Gaussian distributions), the posterior of $\boldsymbol{\theta}$ is also Gaussian, given by:
\begin{align*}
p(\boldsymbol{\theta}|\boldsymbol{D}) \propto \exp\left(-\frac{a}{2}\left(\boldsymbol{y}-\boldsymbol{X}\boldsymbol{\theta}\right)^{T}\left(\boldsymbol{y} - \boldsymbol{X}\boldsymbol{\theta}\right)-\frac{b}{2}\boldsymbol{\theta}^{T}\boldsymbol{\theta}\right) \numberthis 
\end{align*}
Therefore, the posterior has the form $p(\boldsymbol{\theta}|\boldsymbol{D}) = \mathcal{N}_{d}(\boldsymbol{\theta}|\boldsymbol{\mu},\boldsymbol{\Lambda}^{-1})$ where $\boldsymbol{\Lambda}$ denotes the posterior precision matrix (inverse covariance matrix), $\boldsymbol{\mu}$ the posterior mean vector, which are computed as follows:
\begin{align*}
\boldsymbol{\Lambda} &= a\boldsymbol{X}^{T}\boldsymbol{X} + b\boldsymbol{I} \numberthis \\
\boldsymbol{\mu} &= a\boldsymbol{\Lambda}^{-1}\boldsymbol{X}^{T}\boldsymbol{y} \numberthis
\end{align*} 
Thus, for known $a$ and $b$, the posterior of $\boldsymbol{\theta}$ can be easily computed. Even though in real-world applications $a$ is usually not known and a hierarchical model is used instead, the current example is good for testing the utility of our method.

@@

What if the data does not contain any information about a particular parameter? In this case, any good estimation method should detect this, and return the prior of the particular parameter. To test this, we append a random uniform variable $u \sim \mathcal{U}(0, 1)$ to the parameter vector $\boldsymbol{\theta}$ and train the model with this additional dummy parameter. We expect that the networks learn to ignore this dummy parameter, that is, the estimated posterior of $u$ is (approximately) equal to the uniform prior.

@@

During training of the networks, we simulate time-series from the stochastic SIR model with varying lengths. The number of time points $T$ is drawn from a uniform distribution $T \sim \mathcal{U}(200, 500)$ at each training iteration (see the \textbf{SI} for more details about the simulation). Usually, at lower $T$s, the system has not converged to an equilibrium (i.e., not all individuals have transitioned from being $I$ to $R$). Thus, it is especially interesting to see if our method can recover the rate parameters, even if the process dynamics are still unfolding over time. Training the networks took approx. half a day with the active learning approach. Inference on $1000$ datasets with $2000$ posterior samples per parameter took approx. $1.1$ seconds.

@@

\subsection*{Example 4 - Single-Cell RNA Sequencing}
Single-cell RNA sequencing (scRNA-seq) is a method to uncover the dynamics of gene expression within single cells \cite{zappia2017splatter, ozsolak2011rna}. Simulation models for scRNA-seq attempt to mimic the process of sequencing real data samples by combining statistical and algorithmic procedures. The recently developed \textit{Splat} simulation model \cite{zappia2017splatter} implements a hierarchical model where the mean expression levels for multiple genes are samples from a Gamma distribution, and the number of times a gene has been sequenced in a cell is then sampled from a Poisson distribution. The output of the \textit{Splat} simulation is thus a matrix $\boldsymbol{X}$ of \textit{Gene x Cell} counts. \autoref{fig:Fig.7a} depicts the \textit{Splat} algorithm for simulating scRNA-seq data \cite{zappia2017splatter}.
\begin{table} 
\centering
\caption{Splat target parameters estimated by our method}
\begin{tabular}{lll}
Parameter & Name & Description\\
\midrule
$\alpha$ & Mean shape & Shape of the mean gene expression gamma distribution \\
$\beta$ & Mean rate & Rate of the mean gene expression gamma distribution \\
$\mu^{L}$ & Library size location & Location of the library size log-normal distribution \\
$\sigma^{L}$ & Library size scale & Scale of the library size log-normal distribution \\
$\pi^{O}$ & Outlier probability & Probability that a gene is an expression outlier \\
$\mu^{O}$ & Outlier location & Location of the expression outlier factor log-normal distribution \\
$\sigma^{O}$ & Outlier scale & Scale of the expression outlier factor log-normal distribution \\
$\phi$ & Common BCV & Common BCV dispersion across all genes \\
\bottomrule
\end{tabular}
\label{table:Table 1}
\end{table}
As a last example for our method, we use simulations from the \textit{Splat} model and attempt to recover the data-generating parameters. This is a challenging task for any Bayesian method, as the data-generating mechanism is a complicated algorithm, and no likelihood function for joint estimation of the parameters is available. We simulate $200\ 000$  \textit{Gene x Cell} count matrices with different parameter settings (see \textbf{SI} for details of the simulation). Each count matrix contains the information about $40$ genes sequenced in $100$ different cells, that is, each $\boldsymbol{X} \in \mathbb{R}^{40\times100}$. The parameters considered for estimation, along with a short description, are listed in \autoref{table:Table 1}. The parameter estimation task is thus to recover $\boldsymbol{\theta} = (\alpha,\beta,\mu^{L},\sigma^{L},\pi^{O},\mu^{O},\sigma^{O},\phi)$ from an observed count matrix $\boldsymbol{X}$. We train the networks for 50 epochs through the entire dataset and evaluate the performance on a separate validation set of $300$ count matrices. To stabilize training and avoid exploding gradients due to large counts in the input matrices, we apply a log transformation to the data. Simulating the data took approx. $8$ hours. Training the networks took approx. one day with the reference table approach. Inference on $300$ datasets with $2000$ posterior samples per parameter took approx. $1.5$ seconds. 
\begin{figure}[H]
\centering
\begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Splatter_plot.png}
    \caption{The \textit{Splat} simulation diagram. Adapted after \cite{zappia2017splatter}.}
    \label{fig:Fig.7a}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Splatter_scatter.png}
    \caption{Parameter recovery }
    \label{fig:Fig.7b}
\end{subfigure}
\caption[short]{Results on the \textit{Splat} scRNA simulation model. \textbf{(a)} The \textit{Splat} simulation diagram; \textbf{(b)} Parameter recovery.} \label{fig:Fig.7}
\end{figure}
The results on the scRNA example are depicted in \autoref{fig:Fig.7}. We observe excellent parameter recovery on the validation set. \textbf{TODO: Train the full method. These results are preliminary}.

### 2019-07-15 latex/paper_supplementary.tex
Splatter done

\begin{algorithm}
\caption{Simulation-based calibration (SBC) for a single parameter $\theta$ }\label{alg:1}
\begin{algorithmic}[1]
\For{$i = 1,...,n$}
\State {Sample $\tilde{\theta}^{(i)} \sim p(\theta)$}
\State {Simulate a dataset $\boldsymbol{x}^{(i)} = q(\tilde{\theta}^{(i)})$}
\State {Draw posterior samples $\{\theta^{(l)}\}_{l=1}^{L} \sim p(\theta|\boldsymbol{x}^{(i)})$} 
\State {Compute rank statistic $r^{(i)} = \sum_{l=1}^{L}\mathbbm{1}_{[\theta^{(l)}<\tilde{\theta}^{(i)}]}$}
\State {Store $r^{(i)}$}
\EndFor
\State {\textbf{end for}}
\State {Create a histogram of $\{r^{(i)}\}_{i=1}^{n}$ and analyze it for uniformity}
\end{algorithmic}
\end{algorithm}

@@

\section*{Invertible networks}
Throughout all examples, we use a chain of $10$ conditional affine coupling blocks (cACB). Each internal network of each ACB is implemented as a fully connected neural network with $3$ to $4$ hidden layers with $64$ neurons each.

@@

\subsubsection*{Summary network}
We use a permutationally inariant neural network \cite{bloem2019probabilistic} for the \textit{i.i.d.} regression data.

@@

\subsubsection*{Summary network}
We use a bidirectional long short-term memory (LSTM) recurrent neural network for summarizing the Ricker time-series into fixed-size vectors.

@@

\subsubsection*{Summary network}
We use a permutationally invariant neural network \cite{bloem2019probabilistic} for the \textit{i.i.d.} reaction times (RT) data.

@@

\subsubsection*{Summary network}
We use a $1D$ convolutional neural network for summarizing the SIR time-series into fixed-size vectors.

@@

\subsubsection*{Summary network}
We use two permutationally invariant networks \cite{bloem2019probabilistic} for embedding the count matrices generated with the \textit{Splat} simulator \cite{zappia2017splatter} - one running over the cells and one running over the genes dimension.

\subsubsection*{Simulation}
We place the following uniform priors over the parameters of the \textit{Splat} simulation:
\begin{align*}
\beta &\sim \mathcal{U}(0.01, 1) \numberthis \\
\gamma &\sim \mathcal{U}(0.01,\beta)  \numberthis 
\end{align*}
Figure XXX depicts some SIR datasets generated by parameters drawn from the specified priors.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{acb.png}
\caption{Second figure}
\end{figure}

@@

\movie{Type caption for the other movie here. Adding longer text to show what happens, to decide on alignment and/or indentations.}

\movie{A third movie, just for kicks.}

\dataset{dataset_one.txt}{Type or paste caption here.}

\dataset{dataset_two.txt}{Type or paste caption here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}

>>>>

\begin{algorithm}
\caption{Simulation-based calibration (SBC) for a single parameter $\theta$ }\label{alg:1}
\begin{algorithmic}[1]
\For{$i = 1,...,n$}
\State {Sample $\tilde{\theta}^{(i)} \sim p(\theta)$}
\State {Simulate a dataset $\boldsymbol{x}^{(i)} = q(\tilde{\theta}^{(i)})$}
\State {Draw posterior samples $\{\theta^{(l)}\}_{l=1}^{L} \sim p(\theta|\boldsymbol{x}^{(i)})$} 
\State {Compute rank statistic $r^{(i)} = \sum_{l=1}^{L}\mathbbm{1}_{[\theta^{(l)}<\tilde{\theta}^{(i)}]}$}
\State {Store $r^{(i)}$}
\EndFor
\State {\textbf{end for}}
\State {Create a histogram of $\{r^{(i)}\}_{i=1}^{n}$ and inspect it for uniformity}
\end{algorithmic}
\end{algorithm}

@@

\section*{Invertible networks}
Throughout all examples, we use a chain of $10$ conditional affine coupling blocks (cACB). Each internal network of each ACB is implemented as a fully connected neural network with $3$ to $4$ hidden layers with $64$ neurons each. See \href{https://github.com/stefanradev93/cINN}{https://github.com/stefanradev93/cINN} for complete implementation of all networks used throughout this paper.

@@

\subsubsection*{Summary network}
We use the recently introduced permutationally invariant neural network \cite{bloem2019probabilistic} for the \textit{i.i.d.} regression data. This network architecture is a good choice for this example, as each observation is independent of all other, and thus all permutations of a given dataset should lead to the same parameter estimates. Furthermore, invariant networks are independent of the number of observations.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Regression_kl.png}
\caption{KL divergence ($D_{KL}$) between the true and estimated posteriors of the regression weights in our toy Bayesian regression example. The $D_{KL}$ is depicted at every $n$ observations used during training.} 
\end{figure}

@@

\subsubsection*{Summary network}
We use a bidirectional long short-term memory (LSTM) recurrent neural network \cite{gers1999learning} for summarizing the Ricker time-series into fixed-size vectors. The LSTM network architecture is a good choice for this example, as it is able to capture long-term in datasets with temporal or spatial autocorrelations. LSTMs can also easily deal with variable length time-series.

@@

\subsubsection*{Summary network}
We use a permutationally invariant neural network \cite{bloem2019probabilistic} for the \textit{i.i.d.} reaction times (RT) data. Similarly to the toy Regression example, each response in an RT dataset is assumed to be independent of all others, so permutations of the dataset must lead to the same parameter estimates.

@@

\subsubsection*{Summary network}
We use a $1D$ fully convolutional neural network \cite{long2015fully} for summarizing the SIR time-series into fixed-size vectors. Here, we chose a convolutional network architecture over the previously mentioned LSTM, as convolutional networks are more computationally efficient. Further, we wanted to underline the utility of 1D convolutional networks for multidimensional time-series data. Finally, convolutional networks can also deal with variable input sizes.

@@

\subsubsection*{Summary network}
We use a network implementing the recently introduced \textit{self-attention} mechanism \cite{vaswani2017attention}. Self-attention architectures can learn to represent complicated pairwise relationships between observations. This property aligns nicely with the task at hand, since each entry in the observed count matrices is not independent of the other entries. Moreover, these dependencies do not exhibit the typical spatial patterns observed, for instance, in natural images.

\subsubsection*{Simulation}
We place the following uniform priors over the parameters of the \textit{Splat} simulation:
\begin{align*}
\alpha &\sim \mathcal{U}(1, 2) \numberthis \\
\beta  &\sim \mathcal{U}(0.1, 5) \numberthis \\
\mu^{L} &\sim \mathcal{U}(6, 10) \numberthis \\
\sigma^{L} &\sim \mathcal{U}(1, 2) \numberthis \\
\pi^{O} &\sim \mathcal{U}(0.01, 0.5) \numberthis \\
\mu^{O} &\sim \mathcal{U}(0.5, 5) \numberthis \\
\sigma^{O} &\sim \mathcal{U}(0.1, 2) \numberthis \\
\phi &\sim \mathcal{U}(0.1, 0.9) \numberthis 
\end{align*}

@@
